Meta-analysis

### 2019-07-26 05_MetaAnalysis.Rmd
predict missing NAs model is not strong..

#str(PM_MB_means)
```

@@

### Host genotypes
Host genotype may have to be analysed to determine the effect.  
```{r Host_genotype}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>% 
   group_by(host_genotype, Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   kable()

PM_MB_means %>%
   filter(Fungicide == "Tebeconazole") %>%
   group_by(row_spacing,Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   kable()

```
In general the mungbean varieties have the following resistance to powdery mildew.  
   - Berken: Highly susceptible  
   - Crystal: Susceptible  
   - Jade: Moderatly susceptible

@@

log(V)[i] = a + b * log(
   mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
        subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
# need to know what parameters a and b are here
# I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"

>>>>

library(dplyr)
#str(PM_MB_means)
```

@@

### Host genotypes
Host genotype may need to be analysed to determine the effect.  
```{r Host_genotype}
PM_MB_means %>%
   filter(Fungicide == "Tebeconazole",
          row_spacing == 0.75) %>% 
   group_by(host_genotype, Trial_ref) %>%
   summarise() %>%
   count() %>%
   rename(Treatments = n) %>%
   kable()

```
In general the mungbean varieties have the following resistance to powdery mildew.  
   - Berken: Highly susceptible  
   - Crystal: Susceptible  
   - Jade: Moderatley susceptible

@@

log(V)[i] = a + b * log(
   mean(subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "control"),
        subset(PM_MB_means$grain_yield.t.ha.[i], Fungicide == "Tebeconazole")))
# need to know what parameters a and b are here
# I am guessing they represent prediction parameters for each "study" for each of the treatments, "control" and Tebeconazole"
}

# method as described by Emerson
levels(factor(PM_MB_means$Y_error.type))

PM_MB_train <- PM_MB_means %>%
   filter(Y_error.type == "SamplingVariance")

PM_MB_train$Trial_ref <- as.factor(PM_MB_train$Trial_ref)

plot(PM_MB_train$Yield_error, log(as.numeric(PM_MB_train$`grain_yield.t.ha.`)))

library(lme4)

PM_MB_trianLMER <- lmer(log(as.numeric(`grain_yield.t.ha.`)) ~ Yield_error + 
         (1|Trial_ref), data = PM_MB_train)

paramA <- (summary(PM_MB_trianLMER)$coef)[2,1]
InterC <- (summary(PM_MB_trianLMER)$coef)[1,1]

ggplot(PM_MB_train, aes(y = log(as.numeric(`grain_yield.t.ha.`)), x = Yield_error, colour = Trial_ref))+
   geom_point()+
   geom_abline(intercept = InterC, slope = paramA)

exp((log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)) * paramA)+InterC)
# PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$Yield_error
hist(PM_MB_train$Yield_error)
hist(as.numeric(PM_MB_train$`grain_yield.t.ha.`))
hist(log(as.numeric(PM_MB_means[PM_MB_means$Trial_ref == "mung1516/03",]$`grain_yield.t.ha.`)))
